### 2014-11-02 simulation.Rmd
.

## Details
```{r, echo=FALSE, results="hide"}
# For some reason the code doesn't work if we don't print out some of the
# counts, but we can do it in a hidden block.
counttab <- counts(model)
head(counttab)
```

@@

The corresponding plot, where bars are the fit values, and points are the simulated values:
```{r, echo=FALSE, results="asis"}
mr_compare$names <- factor(rownames(mr_compare), levels=rownames(mr_compare))
param_sizes <- floor(log10(abs(mr_compare$simulated)+1e-4)/2)
for (k in unique(param_sizes)) {
    print( ggplot(mr_compare[param_sizes==k,], aes(x=names)) + xlab("") +
        geom_bar(aes(y=fit), stat = "identity", fill="white", color="gray") +
        geom_point(aes(y=simulated)) +
        theme(axis.text.x = element_text(angle = 90),
              axis.title.y = element_blank())
      )
}
```

## residuals for 2-2 Tmers
```{r, echo=FALSE, results="asis"}
resids <- counts_table(in_longwin=2, in_shortwin=2, half_n_show=20)
counts_plot(resids)
```

## residuals for 3-1 Tmers
```{r, results="asis"}
resids <- counts_table(in_longwin=3, in_shortwin=1, half_n_show=20)
counts_plot(resids)
```

## residuals for 9-5 Tmers
```{r, results="asis"}
resids <- counts_table(in_longwin=9, in_shortwin=5, half_n_show=20)
counts_plot(resids)
```

# Pairwise marginal posteriors from MCMC, colored by time in MCMC run
```{r, results="asis", echo=FALSE, fig.align='center', }
if (class(model)=="contextMCMC") {
    subseq <- seq(1,nrow(model@results$batch),length.out=min(1000,nrow(model@results$batch)))
    x <- rbind( model@results$batch[subseq,], mr_compare$simulated[model@results$use.par] ) 
    colnames(x) <- rownames(mr_compare)[model@results$use.par]
    # color by time
    cols <- c( adjustcolor(rainbow(64),.2)[1+floor(65*(1:(nrow(x)-1))/nrow(x))], adjustcolor("black",.5) )
    pairs( x, col=cols, pch=20, cex=c(rep(.5,nrow(x)-1),2) )
} else {
    cat("Not an MCMC run.")
}
```

>>>>

## Details
```{r, include=FALSE}
# For some reason the code doesn't work if we don't print out some of the
# counts, but we can do it in a hidden block.
counttab <- counts(model)
```

@@

The corresponding plot, where bars are the fit values, and points are the simulated values:
```{r, echo=FALSE, results="asis", fig.align='center'}
mr_compare$names <- factor(rownames(mr_compare), levels=rownames(mr_compare))
param_sizes <- floor(log10(abs(mr_compare$simulated)+1e-4)/2)
for (k in unique(param_sizes)) {
    print( ggplot(mr_compare[param_sizes==k,], aes(x=names)) + xlab("") +
        geom_bar(aes(y=fit), stat = "identity", fill="white", color="gray") +
        geom_point(aes(y=simulated)) +
        theme(axis.text.x = element_text(angle = 90),
              axis.title.y = element_blank())
      )
}
```

## residuals for 2-2 Tmers
```{r, echo=FALSE, results="asis", fig.align='center'}
resids <- counts_table(in_longwin=2, in_shortwin=2, half_n_show=20)
counts_plot(resids)
```

## residuals for 3-1 Tmers
```{r, results="asis", fig.align='center'}
resids <- counts_table(in_longwin=3, in_shortwin=1, half_n_show=20)
counts_plot(resids)
```

## residuals for 9-5 Tmers
```{r, results="asis", fig.align='center'}
resids <- counts_table(in_longwin=9, in_shortwin=5, half_n_show=20)
counts_plot(resids)
```

# Trace plot of the MCMC run:
```{r, results="asis", echo=FALSE, fig.width=12, fig.height=7, fig.align='center'}
if (class(model)=="contextMCMC") {
    subseq <- seq(1,nrow(model@results$batch),length.out=min(1000,nrow(model@results$batch)))
    x <- model@results$batch[subseq,]
    colnames(x) <- rownames(mr_compare)[model@results$use.par]
    matplot( model@results$blen*subseq, x, type='l', col=1:5, lty=1:6, xlab='number of MCMC iterations' )
    abline(h=mr_compare$simulated[model@results$use.par], col=1:5, lty=1:6)
    legend("topright",legend=colnames(x),col=1:5,lty=1:6)
} else {
    cat("Not an MCMC run.")
}
```

# Pairwise marginal posteriors from MCMC, colored by time in MCMC run
```{r, results="asis", echo=FALSE, fig.width=12, fig.height=12, fig.align='center'}
if (class(model)=="contextMCMC") {
    subseq <- seq(1,nrow(model@results$batch),length.out=min(1000,nrow(model@results$batch)))
    x <- rbind( model@results$batch[subseq,], mr_compare$simulated[model@results$use.par] ) 
    colnames(x) <- rownames(mr_compare)[model@results$use.par]
    # color by time
    cols <- c( adjustcolor(rainbow(64),.2)[1+floor(65*(1:(nrow(x)-1))/nrow(x))], adjustcolor("black",.5) )
    pairs( x, col=cols, pch=20, cex=c(rep(.5,nrow(x)-1),2), gap=0 )
} else {
    cat("Not an MCMC run.")
}
```
